Automatic Metadata Generation for Fish Specimen Image Collections {\footnotesize \thanks{Research supported by NSF OAC \#1940233 and \#1940322.} }

### 2021-04-07 paper/paper_new.tex
Updates from Overleaf

\section{Introduction}
% Moving teaser since this template doesn't actually ask for one
Over the last several decades advances in computing, imaging, and cyberinfrastructure have supported the growth of digital natural history collections, many of which have specimen images~\cite{beaman2012mass}. Additionally, initiatives, such as the National Science Foundation’s Advancing Digitization of Biodiversity Collections (ADBC) program,
% (which ran for nearly a decade),
have supported the digitization and curation of tens of thousands of biological specimens~\cite{page2015digitization}. These digitized specimens are generally accessible through global, open-access repositories that support digital library services, such as browsing, search and retrieval, and preservation. The digitized renderings of these rich collections permit researchers, educators, students, and the general public to examine biological specimens
on a previously unattainable scale. Moreover, the digitized instantiations present a pathway for applying machine learning and making new scientific discoveries.

Unfortunately, potential scientific advances are hindered by image quality
problems and the lack of accurate and pertinent metadata
associated with the image collections.
Poor quality images (e.g. low contrast, inadequate lighting,
out-of-focus or cluttered visual arrangements) provide inadequate input
for automated
image analysis and machine learning algorithms and lead to inferior
computational results.
In order to perform quantitative morphometric analysis of the specimens,
the physical scale of the images (pixels/inch) is needed; thus
requiring the ability to identify and measure rulers in the images.
Many specimen collections do include Darwin Core metadata~\cite{biodiv_info_standards}, detailing
specimen taxon, geographic location, and several other descriptive aspects.
Additionally, some digitization efforts record technical metadata, detailing imaging specifications. While these types of metadata are helpful for a
human examining several images at a time, they are insufficient for researchers seeking to apply computational methods %machine learning? or okay here
to examine thousands of images
to determine if, for example, a specific fish grows to different lengths
in different habitats, or the temporal evolution of an anatomical feature,
e.g.~the size of a dorsal fin.
\begin{figure*}
  \centering
  \includegraphics[width=.31\linewidth]{images/INHS_FISH_100314}
  \hspace{1mm}
  \includegraphics[width=.31\linewidth]{images/INHS_FISH_100682}
  \hspace{1mm}
  \includegraphics[width=.31\linewidth]{images/INHS_FISH_100020}
  \caption{Three example images from the Illinois Natural History Survey (INHS) collection.}
  \label{fig:INHS_examples}
\end{figure*}

@@

\subsection{Image Contrast}
The contrast of an image is an important image property needed
for the analyses of the BGNN study. Ideally, for INHS images the fish should be well lit and clearly displayed, and the background should also be as light and white as possible.
% Figure~\ref{fig:histo} shows the distribution of
The difference between
the mean intensity of the foreground (i.e.\ the pixels of the fish) and the mean intensity of the background within the fish's bounding box
was computed for all 7,244 images.
The overall mean of the differences is \(144.3\), with a standard deviation of \(15.8\). Images on the low end of the distribution exhibit poor foreground--background contrast, and images on the high end likely contain poorly lit specimens.
Images are considered to have ``low'' and
``high'' contrast if their background-foreground difference is greater than
one standard deviation away from the mean; otherwise they are classified as
``medium''.
Examples of each type of image (low, medium, and high contrast) can be seen in Figure~\ref{fig:contrast}.
The left image has a mean intensity of 103 (low), the middle image 144
(medium), and the right 186 (high).

\begin{table}[H]
    \centering
%    \caption{\verb|foreground.mean| statistics for the three Brightness classes}
    \caption{foreground.mean statistics for the three Brightness classes}
    \label{tab:bright}
    \begin{tabular}{cccc}
        \toprule
        \textbf{Class} & \textbf{Mean Intensity} & \textbf{Standard Deviation} & \textbf{Instances}\\
        \midrule
        Dark & 75.2 & 13.5 & 1800\\
        Normal & 93.6 & 14.8 & 5186\\
        Bright & 108.4 & 15.2 & 242\\
        \bottomrule
    \end{tabular}
\end{table}
\subsection{Brightness}
Specimen brightness is one of the 22 hand-recorded metadata properties. It is encoded as \verb|dark|, \verb|normal| or \verb|bright|. These values
correspond to the mean foreground intensity computed by the automated system.
The mean and standard deviation of the foreground intensities were
computed for the images in the three human-specified classes.
Table~\ref{tab:bright} contains the resulting values and shows that
automated intensities values provide objective measures that may be used to break images into groups that correlate with human-defined brightness
classifications.
The mean of \verb|foreground.mean| over all 7,244 images is 89.5, with a
standard deviation of 16.6. These numbers suggest, for example, that
\verb|foreground.mean| $\pm$ one-half a standard deviation could define 
\verb|normal| brightness, with values outside this range being classified
as \verb|dark| or \verb|bright|.

>>>>

\section{Introduction}
% Moving teaser since this template doesn't actually ask for one
Over the last several decades advances in computing, imaging, and cyberinfrastructure have supported the growth of digital natural history collections, many of which contain specimen images~\cite{beaman2012mass}. Additionally, initiatives, such as the National Science Foundation’s Advancing Digitization of Biodiversity Collections (ADBC) program,
% (which ran for nearly a decade),
have supported the digitization and curation of tens of thousands of biological specimens~\cite{page2015digitization}. These digitized specimens are generally accessible through global, open-access repositories that support digital library services, such as browsing, search and retrieval, and preservation. The digitized renderings of these rich collections permit researchers, educators, students, and the general public to examine biological specimens
on a previously unattainable scale. Moreover, the digitized instantiations present a pathway for applying machine learning and making new scientific discoveries.

Unfortunately, potential scientific advances are hindered by image quality
problems and the lack of accurate and pertinent metadata
associated with the image collections.
Poor quality images (e.g.\ low contrast, inadequate lighting,
out-of-focus or cluttered visual arrangements) provide inadequate input
for automated
image analysis and machine learning algorithms and lead to inferior
computational results.
In order to perform quantitative morphometric analysis of the specimens,
the physical scale of the images (\(\frac{\mathrm{pixels}}{\mathrm{cm}}\)) is needed; thus
requiring the ability to identify and measure rulers in the images.
Many specimen collections do include Darwin Core metadata~\cite{biodiv_info_standards}, detailing
specimen taxon, geographic location, and several other descriptive aspects.
Additionally, some digitization efforts record technical metadata, detailing imaging specifications. While these types of metadata are helpful for a
human examining several images at a time, they are insufficient for researchers seeking to apply computational methods %machine learning? or okay here
to examine thousands of images
to determine if, for example, a specific fish grows to different lengths
in different habitats, or the temporal evolution of an anatomical feature,
e.g.~the size of a dorsal fin.
\begin{figure*}
  \centering
  \includegraphics[width=.31\linewidth]{images/INHS_FISH_100314}
  \hspace{1mm}
  \includegraphics[width=.31\linewidth]{images/INHS_FISH_100682}
  \hspace{1mm}
  \includegraphics[width=.31\linewidth]{images/INHS_FISH_100020}
  \caption{Three example images from the Illinois Natural History Survey (INHS) collection.}
  \label{fig:INHS_examples}
\end{figure*}

@@

\subsection{Image Contrast}
The contrast of an image is an important image property needed
for the analyses of the BGNN study. Ideally, for INHS images the fish should be well lit and clearly displayed, and the background should also be as light and white as possible.
% Figure~\ref{fig:histo} shows the distribution of
The difference between
the mean intensity of the foreground (i.e.\ the pixels of the fish) and the mean intensity of the background within the fish's bounding box
was computed for all \(7,244\) images.
The overall mean of the differences is \(144.3\), with a standard deviation of \(15.8\). Images on the low end of the distribution exhibit poor foreground--background contrast, and images on the high end likely contain poorly lit specimens.
Images are considered to have ``low'' and
``high'' contrast if their background-foreground difference is greater than
one standard deviation away from the mean; otherwise they are classified as
``medium''.
Examples of each type of image (low, medium, and high contrast) can be seen in Figure~\ref{fig:contrast}.
The left image has a mean intensity of 103 (low), the middle image 144
(medium), and the right 186 (high).

\begin{table}[H]
    \centering
%    \caption{\verb|foreground.mean| statistics for the three Brightness classes}
    \caption{foreground.mean statistics for the three Brightness classes}
    \label{tab:bright}
    \begin{tabular}{cccc}
        \toprule
        \textbf{Class} & \textbf{Mean Intensity} & \textbf{Standard Deviation} & \textbf{Instances}\\
        \midrule
        Dark & 75.2 & 13.5 & 1800\\
        Normal & 93.6 & 14.8 & 5186\\
        Bright & 108.4 & 15.2 & 242\\
        \bottomrule
    \end{tabular}
\end{table}
\subsection{Brightness}
Specimen brightness is one of the 22 hand-recorded metadata properties. It is encoded as \verb|dark|, \verb|normal| or \verb|bright|. These values
correspond to the mean foreground intensity computed by the automated system.
The mean and standard deviation of the foreground intensities were
computed for the images in the three human-specified classes.
Table~\ref{tab:bright} contains the resulting values and shows that
automated intensities values provide objective measures that may be used to break images into groups that correlate with human-defined brightness
classifications.
The mean of \verb|foreground.mean| over all \(7,244\) images is 89.5, with a
standard deviation of 16.6. These numbers suggest, for example, that
\verb|foreground.mean| $\pm$ one-half a standard deviation could define 
\verb|normal| brightness, with values outside this range being classified
as \verb|dark| or \verb|bright|.
